### 2018-05-25 4_impl.tex
Add example on invocation hook.

Current version of \porthos[2] contains two invocation hooks, the \texttt{XPorthosInvocationHook} for describing the compatibility-mode functions of the input \porthos[2] input language, and \texttt{XKernelInvocationHook} for describing the Linux kernel-specific functions.
An invocation hook can model any type of operations (memory, fence, computational, etc.).
For instance, the \texttt{XPorthosInvocationHook} intercepts calls \texttt{`location.store(atomic,register)'} and processes the store operation with respect to the specified atomic.
%TODO: more about described functions
%TODO: rename InvocationHook -> XInvocationHook

>>>>

Current version of \porthos[2] contains two invocation hooks, the \texttt{XLegacyInvocationHook} for intercepting the compatibility-mode functions of the \porthos[2] input language, and \texttt{XKernelInvocationHook} for describing the Linux kernel-specific functions.
%Note that the same mechanism (with several modifications) can be used for processing assembly language calls.
An invocation hook can model any type of operations (memory, fence, computational, etc.).
%For instance, the \texttt{XLegacyInvocationHook} intercepts calls \lstinline{`location.store(atomic, register)'} and processes the store operation with respect to the specified atomic.
For instance, the \texttt{XKernelInvocationHook} intercepts the call \lstinline{`WRITE_ONCE(dst_shared, src_local)'} and replaces the invocation with its hook action shown in Figure~\ref{code-invoc-hook}.
%and processes the store operation with respect to the following .

\begin{figure}[!h]
\begin{lstlisting}
class XKernelInvocationHook
       extends XInvocationHookBase 
       implements XInvocationHook {
 ...
 @Override
 public XInvocationHookAction intercept(String functionName) {
   switch (functionName) {
     case "WRITE_ONCE": {
       return new XInvocationHookAction((receiver, arguments) -> {
         if (arguments.length != 2 || receiver != null) {
             return null;  // do not intercept
         }
         XMemoryUnit destUnit = arguments[0];
         if (!(destUnit instanceof XSharedLvalueMemoryUnit)) {
           throw new XMethodInvocationError(methodName, 
               "arg 1: not a shared l-value memory unit: " + destUnit);
         }
         XSharedLvalueMemoryUnit dest = (XSharedLvalueMemoryUnit) destUnit;
         XMemoryUnit srcUnit = arguments[1];
         if (!(srcUnit instanceof XLocalMemoryUnit)) {
           throw new XMethodInvocationError(methodName, 
               "arg 2: not a local memory unit: " + srcUnit);
         }
         XLocalMemoryUnit src = (XLocalMemoryUnit) srcUnit;
         return program.emitMemoryEvent(dest, src);
     });
   }
   case "READ_ONCE": {
     ...
   }
 }
}
\end{lstlisting}
\caption{Example of the invocation hook}
\label{code-invoc-hook}
\end{figure}
